Selecting and ranking interesting pairs of cyclic temporal granularities

### 2020-11-25 paper/main.Rmd
new structure for maintaining simulations

opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
#                                                                read_chunk('main.R')
read_chunk("null_distribution.R")
read_chunk("mean_null.R")
source("R/sim_panel.R")
# Set up plan
#source("_drake.R")
# Run all code required
#drake::r_make()
# load each object as required
# loadd()
```

>>>>

opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
#                                                                read_chunk('main.R')
read_chunk("R/null_distribution.R")
read_chunk("R/mean_null.R")
source("R/sim_panel.R")
# Set up plan
#source("_drake.R")
# Run all code required
#drake::r_make()
# load each object as required
# loadd()
```
